\section{Tell me something new}

Consider a video system for monitoring a highway. Lets say that the
highway is 100 miles long and that we have a 5 cameras per mile,
i.e. 500 cameras. Each camera generates a large raw data stream, on
the order of 1Gbit per second. Using video compression this stream can
be brought down to 1-10Mbit/sec. Totalling .5-5Gbit/sec. A common approach
is to send all of this data to a centralized site where a team of
analysts monitor it to identify accidents, road hazards etc.

Several issues should be noted:
\begin{itemize}
\item A high bandwidth channel is needed to transmit the information
  to the center. If this channel is wireless, this transmission will
  be costly in terms of energy and available bandwidth.
\item Manually monitoring 500 video channels is a very labor intensive task. 
\item Highway traffic is, for the most part, highly
  predictable. Analyst are, for the most part, have no interest in normal traffic. 
  They need to be alerted to {\em abnormalities} such as an accident, a hazardous 
  object on the road or a speeding car.
\end{itemize}

We propose a general framework for designing sensor networks for
anomaly detection called ``tell me something new''~\cite{TMSN}. In
this approach, sensors analyze the data they collect, and send message
to the center only when it estimates that this information is
significantly different than what the center will predict without the
information.

We assume that the cameras are placed at locations and orientations that are fixed for years.
Each camera learns, over time, a predictive model of the traffic on the small segment of 
highway that it observes. Inputs to this model might include time of day, day of week, and day of year, visibility, snow, rain etc. Outputs might include the 


Let $\estate_1(t),\estate_2(t)$ be the estimates of the target
location for each sensor. {\em In addition, each sensor maintains an
  estimate of the estimate of the other sensor.}
$\estate_{1,2}(t),\estate_{2,1}$. Each sensor updates it's estimate of
the velocity of the location of the target according to the signal it
measures, but it does not update it's estimate of the other's
estimate.  If the two estimate are close to each other $\estate_i(t)
\approx \estate_{i,j}(t)$ then sensor $i$ sends no information to
sensor $j$. On the other hand, if $\estate_i(t)$ is far from
$\estate_{i,j}(t)$, then $\estate_{i}$ is transmitted from sensor $i$
to sensor $j$. Thus if the target is moving in constant speed,
uninterrupted, there is not communication between the sensors.

The basic idea here is that a sensor sends out information only if
that information cannot be predicted by the receiver. Similar ideas
have been used in arithmetic coding and \yoav{I think} in
$\Sigma\Delta$ encoding.

Recently, PI Freund~\cite{TMSN} proposed an asynchronous computation
model called ``Tell Me Something New'' in which each agent broadcasts
a message only when the estimate it computes differs from the existing
estimates in a statistically significant way.

 One important application of sensor networks is to monitor activity
 and identify anomalies. Examples include: building security systems,
 factory floors, highway monitoring, health monitoring for the sick or
 elderly and many others.

 On its face, this might seem like an under-constrained impossible
 problem. However, note that for all of the environments listed above
 there is a highly repetitive pattern from day to day and from week to
 week. Add to that the sensors are stationary, and one would expect
 that most sensors observe highly regular and highly predictable
 patterns.
 
 The approach we propose in this case is that each sensor creates a
 model of the characteristics of the signals that it observes during
 normal operations. It alerts neighboring sensors if it observes
 something that is abnormal, i.e. a signal that has very low
 probability according to the model. When several sensors send an
 alert with a short time window, and when the alerts are consistent
 with each other, a global alert is sent to the human operators.

